Beliefs about the development of mental life

### 2021-07-31 supplement/supplement-main.Rmd
add anonymized repo link

---
title: "Beliefs about the development of mental life"
subtitle: "Supplemental materials"
author: "[authors removed to preserve anonymity]"
date: "July 31, 2021"
output:
  # word_document:
  #   reference_docx: word-styles-ref.docx
   bookdown::pdf_document2:
    latex_engine: xelatex
    fig_caption: yes
    toc: true
    toc_depth: 3
bibliography: "references.bib"
# cls: "article.cls"
csl: nature.csl
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{float}
tables: yes
---

@@

Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021]. The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: [removed to preserve anonymity].

>>>>

---
title: "Beliefs about the development of mental life"
subtitle: "Supplemental Materials"
author: "[authors removed to preserve anonymity]"
date: "July 31, 2021"
output:
  # word_document:
  #   reference_docx: word-styles-ref.docx
   bookdown::pdf_document2:
    latex_engine: xelatex
    fig_caption: yes
    toc: true
    toc_depth: 3
bibliography: "references.bib"
# cls: "article.cls"
csl: nature.csl
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{float}
tables: yes
---

@@

Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021]. The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://anonymous.4open.science/r/baby_mental_life_ms-C261/ (repo has been anonymized).
